### 2014-04-24 tab_mr_arfi_axes.tex
updated table headings to reflect B-mode

\begin{table}
\centering
\caption{Comparison of Central Gland / Zone (C) and Total (T) Prostate Axes in MR T2WI and ARFI Imaging.  Axes are approximated in orientation to match those specified in gross pathology: lateral-to-lateral (LL), anterior-to-posterior (AP) and apex-to-base (AB).}
\begin{tabular}{|l|l|l|l|l|l|l|l|l|l|l|l|l|} \hline
{\bf Study} & {\bf MR} & {\bf ARFI} & {\bf MR} & {\bf ARFI} & {\bf MR} & {\bf ARFI} & {\bf MR} & {\bf ARFI} & {\bf MR} & {\bf ARFI} & {\bf MR} & {\bf ARFI} \\ 
{\bf Subject} & {\bf C-AB} & {\bf C-AB} & {\bf C-LL} & {\bf C-LL} & {\bf C-AP} & {\bf C-AP} & {\bf T-AB} & {\bf T-AB} & {\bf T-LL} & {\bf T-LL} & {\bf T-AP} & {\bf T-AP} \\
 & {\bf (cm)} & {\bf (cm)} & {\bf (cm)} & {\bf (cm)} & {\bf (cm)} & {\bf (cm)} & {\bf (cm)} & {\bf (cm)} & {\bf (cm)} & {\bf (cm)} & {\bf (cm)} & {\bf (cm)} \\ \hline
\input{data/axis_data}
\hline
\end{tabular}
\label{tab:mr_arfi_axes}
\end{table}

>>>>

\begin{table}
\centering
\caption{Comparison of Central Gland / Zone (C) and Total (T) Prostate Axes in
    MR T2WI and \textbf{B-mode/}ARFI Imaging.  Axes are approximated in orientation to
    match those specified in gross pathology: lateral-to-lateral (LL),
    anterior-to-posterior (AP) and apex-to-base (AB).}
\begin{tabular}{|l|l|l|l|l|l|l|l|l|l|l|l|l|} \hline
{\bf Study} & {\bf MR} & {\bf ARFI} & {\bf MR} & {\bf ARFI} & {\bf MR} & {\bf ARFI} & {\bf MR} & {\bf B-mode} & {\bf MR} & {\bf B-mode} & {\bf MR} & {\bf B-mode} \\ 
{\bf Subject} & {\bf C-AB} & {\bf C-AB} & {\bf C-LL} & {\bf C-LL} & {\bf C-AP} & {\bf C-AP} & {\bf T-AB} & {\bf T-AB} & {\bf T-LL} & {\bf T-LL} & {\bf T-AP} & {\bf T-AP} \\
 & {\bf (cm)} & {\bf (cm)} & {\bf (cm)} & {\bf (cm)} & {\bf (cm)} & {\bf (cm)} & {\bf (cm)} & {\bf (cm)} & {\bf (cm)} & {\bf (cm)} & {\bf (cm)} & {\bf (cm)} \\ \hline
\input{data/axis_data}
\hline
\end{tabular}
\label{tab:mr_arfi_axes}
\end{table}

### 2014-04-24 tab_mr_arfi_volumes.tex
updated table headings to reflect B-mode

\begin{table}[h!]
\centering
\caption{Comparison of Central Gland / Zone and Total Prostate Volumes in MR T2WI and ARFI Imaging}
\begin{tabular}{|l|l|l|l|l|} \hline
{\bf Study Subject} & {\bf MR Central Gland} & {\bf MR Total} & {\bf ARFI Central Gland} & {\bf ARFI Total} \\ 
& {\bf Volume (cm$^3$)} & {\bf Volume (cm$^3$)} & {\bf Volume (cm$^3$)} & {\bf Volume (cm$^3$)} \\ \hline
\input{data/vol_data}
\hline
\end{tabular}
\label{tab:mr_arfi_volumes}
\end{table}

>>>>

\begin{table}[h!]
\centering
\caption{Comparison of Central Gland / Zone and Total Prostate Volumes in MR T2WI and \textbf{B-mode/}ARFI Imaging}
\begin{tabular}{|l|l|l|l|l|} \hline
{\bf Study Subject} & {\bf MR Central Gland} & {\bf MR Total} & {\bf ARFI Central Gland} & {\bf B-mode Total} \\ 
& {\bf Volume (cm$^3$)} & {\bf Volume (cm$^3$)} & {\bf Volume (cm$^3$)} & {\bf Volume (cm$^3$)} \\ \hline
\input{data/vol_data}
\hline
\end{tabular}
\label{tab:mr_arfi_volumes}
\end{table}
